%
%  Title       :  System design document
%  Authors     :  Alex Gerdes
%  Created     :  August 20, 2018
%
%  Purpose     :  Tempate SDD for TDA367/DIT212
%
%-------------------------------------------------------------------------------

\documentclass[12pt,a4paper]{scrartcl}

\usepackage[hyphens]{url}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{mathpazo}

\title{System design document for \ldots}
\author{authors}
\date{date\\version}

\begin{document}

\maketitle

\section{Introduction}

General info. What is this? What does it describe?

\subsection{Definitions, acronyms, and abbreviations}

Some definitions etc. probably same as in RAD


\section{System architecture}

The most overall, top level description of the system. Which (how many)
machines are involved? What are the system components, and what are they 
responsible for? Show the dependency between the different system components.
If there are more computing entities (machines) involved: show dow they 
communicate. Describe the high level overall flow of some use stories. Describe
how to start and stop the system.

Any general principles in application? Flow, creations, \ldots


\subsection{Subsystem decomposition}

Describe in this section each identified system component (that you have implemented).

\subsection{`first component'}

What is this component responsible for and what does it do.

Divide the component into subsystems (packages) and describe their
responsibilities. Draw an UML package diagram for the top level. Describe the
interface and dependencies between the packages. Try to identify abstraction
layers. Think about concurrency issues.

If your application is a standalone then:
\begin{itemize}
  \item Describe how MVC is implemented
  \item Describe your design model (which should be in one package and
    build on the domain model)
  \item Give a class diagram for the design model.
\end{itemize}
otherwise:
\begin{itemize}
  \item MVC and domain model described at System Architecture
\end{itemize}

Diagrams
\begin{itemize}
  \item Dependencies (\href{http://stan4j.com/}{STAN} or similar)
  \item UML sequence diagrams for flow.
  \item Describe which design patterns you have applied.
\end{itemize}

Quality
\begin{itemize}
  \item List of tests (or description where to find the test)
  \item Quality tool reports, like \href{http://filehippo.com/download_pmd/}{PMD} (known issues listed here)
\end{itemize}

NOTE: Each Java, XML, etc. file should have a header comment: Author,
responsibility, used by ..., uses ..., etc.

\subsection{`next component'}

As above, and continue for all components.


\section{Persistent data management}

How does the application store data (handle resources, icons, images, audio,
...). When? How? URLs, pathe’s, ... data formats... naming..


\section{Access control and security}

Different roles using the application (admin, user, ...)? How is this handled?


\section{References}


\end{document}
